Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-11-01 manuscript/manuscript.Rmd

In Figure \@ref(fig:pdp), we exhibit the PDP for the "vehicle age" variable.
We see that the average predicted loss cost decreases with vehicle age until
the latter is around 18. Note that the rug on the $x$-axis tell us that the
data is quite thin for vehicle age greater than 18, so the apparent upward
trend to the right is driven by just a few data points.

@@

This work is supported by the Casualty Actuarial Society.

>>>>

In Figure \@ref(fig:pdp), we exhibit the PDP for the "vehicle age" variable.
We see that the average predicted loss cost decreases with vehicle age until
the latter is around 18. Note that the accompanying histogram shows that the
data is quite thin for vehicle age greater than 18, so the apparent upward
trend to the right is driven by just a few data points.

@@

We thank Navdeep Gill for his presentation on interpretable ML at SDSS and
helpful follow-up discussions, and Daniel Falbel for his assistance with R and 
TensorFlow.
This work is supported by the Casualty Actuarial Society.
